### 2014-04-02 LaTeX/PreezeText.tex
Fixed name. Added question.

\begin{itemize}
	\item When and why do states comply with economic sanctions? 
	\item We demonstrate the necessity of incorporating network dynamics into understanding the time until sanction compliance
	\item We show that the connectivity between target and sender states--in terms of cultural similarities, geographical proximity, and alliance patterns--plays an important and previously overlooked role on sanction outcomes
\end{itemize}

>>>>

Why do some states facing internal armed conflict suffer severe economic consequences while others enjoy continued growth?
